### 2020-02-06 method/sec_5-data_preprocess.tex
Added All 1440 result graphs

\section{Extensions (Weather Data Prepossessing)}
The data imported via imported modules may have incorrect data, missing data and not compatible with directly feed into simulation modules. 
Thus it required to preprocess data before going to use in such cases. The WDIAS supports these capabilities via Extensions. Current system has
in build few extensions such as Interpolation, Transformation and Validation. Other than those, it possible to add more extensions as required.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
    \caption{Weather Data Preprocessing}
    \label{fig:weather_data_preprocessing}
\end{figure}
The WDIAS provides the support via in build simple generic mathematical function structure. Each extension is considering as a mathematical function which can take p 
number of input timeseries variables and output n number of timeseries variables. Other than that, at the time of processing the system can configure to provide
bind constant which can provide while configuring an extension. Which means, it is possible to change the behaviour of a existing function by providing different bind
constant at the time of creating new tiggers for an extension.

>>>>

\section{Extensions (Weather Data Prepossessing)}
The data imported via imported modules may have incorrect data, missing data and not compatible with directly feed into simulation modules. 
Thus it required to preprocess data before going to use in such cases. The WDIAS supports these capabilities via Extensions. Current system has
in build few extensions such as Interpolation, Transformation and Validation. Other than those, it possible to add more extensions as required.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
    \caption{Weather Data Preprocessing}
    \label{fig:weather_data_preprocessing}
\end{figure}
The WDIAS provides the support via in build simple generic mathematical function structure. Each extension is considering as a mathematical function which can take p 
number of input timeseries variables and output n number of timeseries variables. Other than that, at the time of processing the system can configure to provide
bind constant which can provide while configuring an extension. Which means, it is possible to change the behaviour of a existing function by providing different bind
constant at the time of creating new triggers for an extension.

### 2020-02-06 results/sec_2-work_load.tex
Added All 1440 result graphs

\subsubsection{Performance Tuning}
In order to get better performance using the available resources, it is possible to schedule each microservice into a predefined set of nodes. There are few ways to do in the \acrshort{k8s};
\begin{itemize}
    \item \emph{nodeSelector} - Hard rules match for node schedule. If not match, pods will not schedule.
    \item \emph{node Affinity and Anti-Affinity} - Soft rules for node schedule. Based on the rules, pods will schedule on most appropriate node.
    \item \emph{Taints and Tolerations} - Opposite of nodeSelector, repel mismatching pods away from the nodes.
\end{itemize}
Users can use one of above features to fine-tune the \acrshort{wdias} to perform better. For the moment, \acrshort{wdias} helm charts uses node Affinity in order to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes. Pods are assigned to the nodes \ref{tab:aws_eks_nodes} based on the node label as below;
\begin{itemize}
    \item \emph{core}: metadata, extensions, query, status and extension services
    \item \emph{grid}: grid adapter, import and export grid data
    \item \emph{scalar}: scalar and vector adapters, import and export of same data types
    \item \emph{test}: jmeter and metric server
\end{itemize}
The databases uses for data consistency and performance in storage optimization with search capabilities. But because of that, it only possible to run one instance of those. In the \acrshort{wdias}, the MySQL and MongoDb are not getting higher load as adapter databases such as InfluxDB for scalar and vector data types, and netCDF for grid data type. In order to keep up with the pace, those microservice pods are assign to dedicated nodes in order to increase the performance of inter-service communication.

>>>>

\subsubsection{Performance Tuning}
In order to get better performance using the available resources, it is possible to schedule each microservice into a predefined set of nodes. There are few ways to do in the \acrshort{k8s};
\begin{itemize}
    \item \emph{nodeSelector} - Hard rules match for node schedule. If not match, pods will not schedule.
    \item \emph{node Affinity and Anti-Affinity} - Soft rules for node schedule. Based on the rules, pods will schedule on most appropriate node.
    \item \emph{Taints and Tolerations} - Opposite of nodeSelector, repel mismatching pods away from the nodes.
\end{itemize}

- e.g., diagram indicating the nodes and their connectivity (load generator, target, storage, etc.), Then briefly describe the diagram.

Users can use one of above features to fine-tune the \acrshort{wdias} to perform better. For the moment, \acrshort{wdias} helm charts uses node Affinity in order to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes. Pods are assigned to the nodes \ref{tab:aws_eks_nodes} based on the node label as below;
\begin{itemize}
    \item \emph{core}: metadata, extensions, query, status and extension services
    \item \emph{grid}: grid adapter, import and export grid data
    \item \emph{scalar}: scalar and vector adapters, import and export of same data types
    \item \emph{test}: jmeter and metric server
\end{itemize}
The databases uses for data consistency and performance in storage optimization with search capabilities. But because of that, it only possible to run one instance of those. In the \acrshort{wdias}, the MySQL and MongoDb are not getting higher load as adapter databases such as InfluxDB for scalar and vector data types, and netCDF for grid data type. In order to keep up with the pace, those microservice pods are assign to dedicated nodes in order to increase the performance of inter-service communication.
